\documentclass[10pt,a4paper,sans]{moderncv}

% ModernCV Theme: Classic
\moderncvstyle{classic} 
\moderncvcolor{blue}

% Font: Lato (Modern, Geometric, Clean)
\usepackage[default]{lato} 

% Icons: Upgraded to FontAwesome5 for a modern look
\usepackage{fontawesome5}

% Colors: Custom "Electric Blue" for a sharper, digital-first look
\usepackage{xcolor}
\definecolor{techblue}{HTML}{2563eb} % Electric Blue (Vibrant)
\definecolor{darkgray}{HTML}{0f172a} % Slate-900 (High Contrast)
\definecolor{lightgray}{HTML}{64748b} % Slate-500 (Soft)

% Apply custom colors
\colorlet{color1}{techblue}
\colorlet{color2}{darkgray}

% Enforce Bold Section Headers for a sharper look
\renewcommand*{\sectionfont}{\Large\bfseries\upshape}

% Adjust column width for the timeline
\setlength{\hintscolumnwidth}{3.2cm} 

% Margins: Optimized
\usepackage[scale=0.92, top=1.2cm, bottom=1.2cm, left=1.2cm, right=1.2cm]{geometry}

% Character encoding
\usepackage[utf8]{inputenc}

% Custom list spacing
\usepackage{enumitem}
\setlist[itemize]{label=\textcolor{techblue}{\textbullet}, nosep, leftmargin=*, before=\vspace{-0.15em}, after=\vspace{-0.15em}}

% Explicitly configure hyperref to ensure links are clickable and colored correctly
\AtBeginDocument{
    \hypersetup{
        colorlinks=true,
        linkcolor=techblue,
        urlcolor=techblue,
        pdftitle={Wutcharin Thatan - Resume},
        pdfauthor={Wutcharin Thatan}
    }
}

% Personal Data
\name{Wutcharin}{Thatan}
\title{Executive Leader | AI, Automation \& Analytics} 
\phone[mobile]{(+66) 061-565-5969}
\email{wutcharin.th@gmail.com}
\social[linkedin]{Wutcharin}
\extrainfo{\href{https://wutcharin.com}{https://wutcharin.com}}

\begin{document}

% --- CUSTOM LEFT-ALIGNED HEADER ---
\begin{minipage}[t]{0.70\textwidth}
    \vspace*{-0.5cm}
    % Name in single color (Tech Blue)
    {\fontsize{28}{32}\selectfont\bfseries\textcolor{techblue}{Wutcharin Thatan}}\\[0.2cm]
    {\fontsize{12}{14}\selectfont\textcolor{lightgray}{Executive Leader | AI, Automation \& Analytics}}\\[0.3cm]
    {\small\textcolor{darkgray}{
    \faMapMarker~ Bangkok, Thailand \quad
    \faMobile~ (+66) 061-565-5969 \quad
    \faEnvelope~ \href{mailto:wutcharin.th@gmail.com}{wutcharin.th@gmail.com} \\
    \faLinkedin~ \href{https://linkedin.com/in/Wutcharin}{Wutcharin} \quad
    \faGlobe~ \href{https://wutcharin.com}{https://wutcharin.com}
    }}
\end{minipage}
\hfill
\begin{minipage}[t]{0.28\textwidth}
   % Clean modern look without photo
\end{minipage}

\vspace{0.5cm}
\begin{center}
    \textit{\textcolor{techblue}{"Transforming businesses through AI-powered automation, advanced analytics, and intelligent data solutions."}}
\end{center}
\vspace{0.3cm}

%--- Executive Profile ---
\section{Executive Profile}
\cvitem{}{
Executive leader with nearly 20 years of experience (10+ in people management), possessing a \textbf{unique combination of Business Strategy and Technical Execution expertise}. Specialized in \textbf{scaling high-performing AI, Automation, and Analytics functions}, I am a hands-on builder who translates complex data into C-suite strategies, having secured \textbf{200M THB in capital} via data-driven planning. Expert in bridging the gap between Finance, Engineering, and Commercial strategy in both hyper-growth Tech (Agoda) and Aviation sectors.
}

%--- Competencies ---
\section{Key Competencies \& Technical Skills}
\cvitem{\textbf{Leadership}}{Corporate Data Strategy, AI Roadmaps, C-Suite Advisory, Venture Fundraising, Crisis Management, Corporate Turnarounds, Team Building (Managed teams of 8-11 specialists).}
\cvitem{\textbf{AI \& Dev}}{Generative AI (Gemini, Claude), RAG Architectures, AI Agents (Text-to-SQL), React, Node.js, Python, n8n, Firebase.}
\cvitem{\textbf{Analytics}}{SQL, Tableau, Metabase, Predictive Modeling (\textbf{Time Series, Regression, Classification, Clustering}), ETL Pipelines, Financial Variance Analysis.}

%--- Featured Projects ---
\section{Featured AI Projects}
\cvitem{SplitBill AI}{\textbf{Creator \& Developer} | \href{https://splitbill-ai.com}{splitbill-ai.com} \newline
Built a production-ready AI expense splitter end-to-end in \textbf{7 days}. Features instant receipt scanning via \textbf{Gemini AI}, automatic item parsing, and smart user assignment. \textit{Tech Stack: React, Firebase, Google AI Studio.}}

\cvitem{LocalGuide}{\textbf{Full Stack Developer} | \href{https://web-production-c4714.up.railway.app}{Live Prototype Link} \newline
Designed and built the MVP for a friend's travel tech startup to connect tourists with local experts. Engineered the full-stack architecture including secure authentication, dynamic profile management, and booking workflows. \textit{Tech Stack: React, Express.js, PostgreSQL, Railway.}}

%--- Professional Experience ---
\section{Professional Experience (Last 10 Years)}

\cventry{Apr 2024 -- Present}{Associate Director - FinTech Data and Automation}{Agoda}{Bangkok}{}{
\begin{itemize}
    \item \textbf{Strategic Leadership:} Lead the FinTech Data and Automation (FDA) division, comprised of an \textbf{8-person team} across Finance Analytics and RPA/AI. Drive operational efficiencies across critical functions including \textbf{Treasury, Tax, and Credit Risk}.
    \item \textbf{Impact:} Achieved \textbf{12,000 hours in annual productivity gain} by implementing targeted automation and data-driven process improvements, significantly reducing manual workload in financial reconciliation.
    \item \textbf{Vision:} Define and execute the long-term AI, Automation, and Analytics vision for FinTech, championing advanced analytics and self-service BI tools to embed a data-first culture within the finance organization.
\end{itemize}}
\vspace{2mm} % Adjusted spacing

\cventry{Apr 2023 -- Feb 2024}{Head of Commercial}{Really Cool Airlines}{Bangkok}{}{
\begin{itemize}
    \item \textbf{Startup Launch:} Built and mentored a high-performing commercial division of \textbf{11 professionals} from the ground up, establishing \textbf{6 teams} including Network Planning, Revenue Management, Commercial Operations, and Marketing.
    \item \textbf{Fundraising:} Translated complex market data into a compelling vision and investor pitch, leveraging insights from \textbf{fleet and schedule planning} to secure \textbf{200M THB} in seed funding to launch the airline.
    \item \textbf{Strategy:} Foster a culture of excellence and innovation, setting the strategic direction for route planning and business development.
\end{itemize}}
\vspace{2mm} % Adjusted spacing

\cventry{Apr 2022 -- Mar 2023}{Head of Strategic Foresight \& Planning}{Thairath Group}{Bangkok}{}{
\begin{itemize}
    \item \textbf{Transformation:} Managed a \textbf{team of PMOs} and led a data-driven culture project, implementing KPI frameworks and analytics systems that unified strategic priorities across diverse business units.
    \item \textbf{Advisory:} Advised on resource allocation, inter-departmental communication, and technology decisions to drive group-level goals. Launched a new media business unit by developing plans to mitigate content rights risks.
\end{itemize}}
\vspace{2mm} % Adjusted spacing

\cventry{Nov 2017 -- Apr 2022}{Associate Director - Supply Analytics}{Agoda}{Bangkok}{}{
\textit{Career Progression: Senior Opportunity Manager (2017) $\to$ Head of Analytics (2019) $\to$ Associate Director (2021)}
\begin{itemize}
    \item \textbf{Analytics Leadership:} Led a team of \textbf{7 analysts} across Partner Programs and the Agoda Display Network. Partnered with MIS on database/dashboard development and presented KPI insights to senior leaders.
    \item \textbf{Cross-Functional Collaboration:} Collaborated intensively with \textbf{Sales, Account Management, and Product teams} on new product launches, sales strategies, and goal setting.
    \item \textbf{Innovation:} Built credit risk models and protocols. Evaluated business opportunities and formulated optimization strategies to support Regional Account Management.
    \item \textbf{Scale:} Oversaw the development and delivery of a comprehensive self-service analytics ecosystem, including \textbf{100+ Tableau dashboards for 600+ users}.
\end{itemize}}
\vspace{2mm} % Adjusted spacing

\cventry{Oct 2016 -- Nov 2017}{Planning Director}{Nok Air}{Bangkok}{}{
\begin{itemize}
    \item \textbf{Corporate Turnaround:} Co-architected a successful corporate turnaround using analytical models to increase aircraft utilization by \textbf{15\%}. Led \textbf{route network planning, financial modeling}, and competitive analysis to design multi-year strategic plans.
    \item \textbf{Capital Secured:} Developed and presented the comprehensive turnaround strategy to the Board of Directors, lessors, banks, and potential investors, securing critical new investment.
\end{itemize}}
\vspace{2mm} % Adjusted spacing

\cventry{Nov 2015 -- Sep 2016}{Strategy \& Planning Manager}{Thai Smile Airways}{Bangkok}{}{
\begin{itemize}
    \item \textbf{Network Strategy:} Managed a team of 8 on network optimization, route expansion, and strategic planning. Monitored KPIs and provided recommendations to senior leadership.
    \item \textbf{Relations:} Built and maintained critical relationships with aviation authorities and government bodies to secure vital operating permits and slots.
\end{itemize}}

%--- Education ---
\section{Education}
\cventry{2013 -- 2015}{Master of Business Administration}{Stamford International University}{}{}{}
\cventry{2004 -- 2008}{Bachelor of Engineering}{Chulalongkorn University}{}{}{}

\end{document}
